%Define document class:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt,a4paper,oneside]{book}

%Include the required packages to be used in the document:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[top=4cm,right=2.5cm,bottom=2.5cm,left=2.5cm]{geometry}
% \usepackage[headings]{fullpage}
\usepackage{setspace}
\usepackage{graphicx,wrapfig,lipsum}
\usepackage{float}
\usepackage{array}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{appendix}
\usepackage[pdfborder={0 0 0}, colorlinks=true, linkcolor=black, citecolor=blue, urlcolor= black]{hyperref}
\usepackage[printonlyused]{acronym}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{ifpdf}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{subcaption}
\usepackage{times}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{multirow}
%\usepackage[square, numbers, comma, sort&compress]{natbib}
%\usepackage{notoccite}
%\usepackage{subfig}
%\usepackage{xtab}
%\usepackage{accents}
%\usepackage[backend=bibtex]{biblatex}
%\usepackage{rotating}
%\usepackage{tabularx}
%\usepackage{capt-of}% or use the larger `caption` package
%\usepackage{longtable}
%\usepackage{fancyhdr}
%\setlength{\headheight}{20pt} 
%\usepackage{graphics}
%\usepackage{epstopdf}



% \include{Sections/01_class_and_packages}
% \include{Sections/02_new_commands}
\include{Sections/03_Authors_info} %change your info
\begin{document}
\include{Sections/04_titlepage} %change number of supervisors, Date
% \include{Sections/05_list_publications}
% \include{Sections/06_funny_quote}
\include{Sections/07_declaration} %change degree
\include{Sections/08_acknowledgments}
\include{Sections/09_abstract}
\include{Sections/10_toc_figures_tables}
% \include{Sections/11_dedication}

\pagestyle{headings}
\pagenumbering{arabic}
%include chapters in the following part:
%========================================
\include{chapters/introduction}
\include{chapters/background}
\include{chapters/Methodology}
\include{chapters/results}
\include{chapters/conclusion}
% \include{chapters/future_work}









%Add the appendix here:
%==========================
% \include{chapters/appendix}     

\pagebreak
%Add the bibliography here:
%=============================
\begin{thebibliography}{00}
\bibitem{pid} Emirler, Mümin Tolga, et al. "Robust PID steering control in Parameter Space for highly automated driving." International Journal of Vehicular Technology 2014 (2014).
\bibitem{mpc} Rafaila, Razvan C., Constantin F. Caruntu, and Gheorghe Livint. "Nonlinear model predictive control using Lyapunov functions for vehicle lateral dynamics." IFAC-PapersOnLine 49.3 (2016): 135-140.
\bibitem{nvidia} Bojarski, Mariusz, et al. "End to end learning for self-driving cars." arXiv preprint arXiv:1604.07316 (2016).
\bibitem{nvidia_activ} Bojarski, Mariusz, et al. "Explaining how a deep neural network trained with end-to-end learning steers a car." arXiv preprint arXiv:1704.07911 (2017).
\bibitem{visualbackprop} Bojarski, Mariusz, et al. "VisualBackProp: efficient visualization of CNNs." arXiv preprint arXiv:1611.05418 (2016).
\bibitem{alvinn} Pomerleau, Dean A. "Alvinn: An autonomous land vehicle in a neural network." Advances in neural information processing systems. 1989.
\bibitem{dave} LeCun, Y., et al. DAVE: Autonomous off-road vehicle control using end-to-end learning. Technical Report DARPA-IPTO Final Report, Courant Institute/CBLL, http://www. cs. nyu. edu/yann/research/dave/index. html, 2004.
\bibitem{viz} Zeiler, Matthew D., and Rob Fergus. "Visualizing and understanding convolutional networks." European conference on computer vision. Springer, Cham, 2014.
\bibitem{ipopt} Wächter, Andreas, and Lorenz T. Biegler. "On the implementation of an interior-point filter line-search algorithm for large-scale nonlinear programming." Mathematical programming 106.1 (2006): 25-57.
\bibitem{adam} Kingma, Diederik P., and Jimmy Ba. "Adam: A method for stochastic optimization." arXiv preprint arXiv:1412.6980 (2014).
\bibitem{kitti} Geiger, Andreas, et al. "Vision meets robotics: The KITTI dataset." The International Journal of Robotics Research 32.11 (2013): 1231-1237.
\bibitem{kitti_road} Fritsch, Jannik, Tobias Kuhnl, and Andreas Geiger. "A new performance measure and evaluation benchmark for road detection algorithms." Intelligent Transportation Systems-(ITSC), 2013 16th International IEEE Conference on. IEEE, 2013.
\bibitem{gti} Arróspide, Jon, Luis Salgado, and Marcos Nieto. "Video analysis-based vehicle detection and tracking using an mcmc sampling framework." EURASIP Journal on Advances in Signal Processing 2012.1 (2012): 2.
\bibitem{backprop} Baydin, Atilim Gunes, et al. "Automatic differentiation in machine learning: a survey." arXiv preprint arXiv:1502.05767 (2015).
\bibitem{vgg} Simonyan, Karen, and Andrew Zisserman. "Very deep convolutional networks for large-scale image recognition." arXiv preprint arXiv:1409.1556 (2014).
\end{thebibliography}

\end{document}
